Supplementary Content

### 2022-02-21 experiments/2_supplement/supplement.Rmd
Prtly fix for #21
fixed supplement figure issue

As is shown in the figures below, the temporal method results in a larger region of bistability than the replication method, but only during increasing oxygen diffusivities. The difference in results occurs because, as mentioned above, the initial conditions differ between the two approaches. For example, in the temporal method, the oxygen concentration in the anoxic state is lower than the initial oxygen concentration in the replication approach, and **Owen guesses that** the sulfide concentration is higher **check that last statement**.

@@

(ref:repl-meth2) Stable states found with the *replication* method. The solid (down) line refers to the stable state when cyanobacteria begin at high abundance (favouring the oxic state). The dashed up line refers to when their initial abundnace is low (favouring the anoxic state). Please note: i) that near vertical lines indicate the position of a tipping point and hence the system cannot exist on point of that part of the line; ii) the separatrix (the unstable equilibrium) is not shown.

```{r repl-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:repl-meth2)', fig.height=8, fig.width=8, fig.align="center"}
## To be completed.
plot_ss_result1(repl_meth,
                result_index = 1,
                filename_prefix = NULL,
                save_image_file = FALSE)

## Would like to here use the function fig_state_vs_o2diff_sidebyside_dots() (as is used in the next chunk) but there is some incompatibility as the function was written for results from the temporal method, and does not work for those from the replication method. Rainer, could you please see if you can make a workaround?

@@

(ref:temp-meth2) Stable states found with the *temporal* method. All other aspects are the same as in Figure \@ref(fig:repl-meth1).

@@

```{r ss-temp-meth3, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth3)', fig.height=8, fig.width=8, fig.align="center"}
single_1e6 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/single_1e6_result.RDS"))
only_SB_variable[13,]$ssfind_result[[1]] <- single_1e6
fig_state_vs_o2diff_sidebyside_dots(only_SB_variable[13,])
```

@@

```{r ss-temp-meth4, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth4)', fig.height=8, fig.width=8, fig.align="center"}
single_2e6 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/single_2e6_result.RDS"))
only_SB_variable[13,]$ssfind_result[[1]] <- single_2e6
fig_state_vs_o2diff_sidebyside_dots(only_SB_variable[13,])
```

>>>>

As is shown in the figures below, the temporal method results in a larger region of bistability than the replication method, but only during increasing oxygen diffusivities. The difference in results occurs because, as mentioned above, the initial conditions differ between the two approaches.

@@

(ref:repl-meth2) Stable states found with the *replication* method. The right column of panels refers to the stable state when oxygen diffusivity is at first high (favouring the oxic state). The left column refers to when oxygen diffusivity is at first low (favouring the anoxic state). Points (which sometimes are so close as to appear as thick lines) show the stable state at the end of each period of constant oxygen diffusivity. Thin lines are for visualisation only, and join the points. Grey arrows show the oxygen diffusivity at which the system flips, and the direction of the flip. The length of the grey arrows is without meaning.

```{r repl-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:repl-meth2)', fig.height=8, fig.width=8, fig.align="center"}
fig_state_vs_o2diff_sidebyside_dots(repl_meth[1,])
```

@@

(ref:temp-meth2) Stable states found with the *temporal* method. All other aspects are the same as in Figure \@ref(fig:repl-meth2).

@@

```{r ss-temp-meth3, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth3)', fig.height=8, fig.width=8, fig.align="center"}
single_1e6 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/single_1e6_result.RDS"))
temp_meth[1,]$ssfind_result[[1]] <- single_1e6
fig_state_vs_o2diff_sidebyside_dots(temp_meth[1,])
```

@@

```{r ss-temp-meth4, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth4)', fig.height=8, fig.width=8, fig.align="center"}
single_2e6 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/single_2e6_result.RDS"))
temp_meth[1,]$ssfind_result[[1]] <- single_2e6
fig_state_vs_o2diff_sidebyside_dots(temp_meth[1,])
```
